Viscous Erosion in Porous Media

### 2018-03-11 docs/methods/erosion_methods.tex
NM

We now discuss some physical aspects of multi-body erosion revealed by our simulations. In Fig.~\ref{fig:06bodies} we show a simulation of 6 eroding bodies, each initially circles of various sizes and positions. Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable. As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable (such as the foremost and aft-most points on the body). Rather, when and where these sharp features develop depends on inter-body feedback as mediated by the Stokes flow.

@@

The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several near contacts between bodies, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6. Our method handles these near contacts without difficulty. Interestingly, erosion appears to preferentially remove material from these regions of near contact, as the narrow spacing between bodies expands rather rapidly. For example, the spacing between bodies 1 \& 2 was initially very small but is already comparable to the spacing between bodies 3 \& 4 by the second frame. Even more interesting, the bodies tend to develop flat faces wherever near contact occurs, which leads to the appearance of straight channels in between bodies. Such channels are apparent between bodies 1 \& 2, 3 \& 5, and 5 \& 6, and they {persist} for the duration of the simulation.

The vorticity field (color) is useful to infer both the regions of highest shear and the regions of most intense flow. Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel running horizontally, below bodies 1 \& 2 and above bodies 3 \& 6. This main channel widens the fastest as the high-flow rate leads to greater shearing on the boundaries. As discussed above, the pressure drop across the cell is fixed in these simulations, and so as the bodies diminish the flow rate increases, which can be seen by the increase in the vorticity magnitude. By the final frame shown, body 4 has vanished completely and our method handles this event seamlessly.

>>>>

We now discuss some physical aspects of multi-body erosion revealed by our simulations. Figure~\ref{fig:06bodies} shows a simulation of 6 eroding bodies, each initially circles of various sizes and positions. Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable. As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable. Rather, when and where these sharp features develop depends on inter-body feedback as mediated by the Stokes flow.

@@

The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several near contacts between bodies, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6. Our method handles these near contacts without difficulty. Interestingly, erosion appears to preferentially remove material from these regions of near contact, as the narrow spacing between bodies expands rather rapidly. For example, the spacing between bodies 1 \& 2 is initially very small, but by the second frame, is comparable to the spacing between bodies 3 \& 4. Even more interesting, the bodies tend to develop flat faces where there are near contacts. This effect leads to the appearance of straight channels in between bodies, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6. Once formed, these straight channels persist until the bodies have nearly vanished.

The vorticity field not only allows us to visualize regions of high shear, but also allows us to identify preferred channels with most intense flow. Figure~\ref{fig:06bodies} shows that the flow is concentrated primarily in a single channel that runs horizontally below bodies 1 \& 2 and above bodies 3, 5, \& 6. This main channel widens the fastest, and secondary channels (e.g.~between bodies 1 \&2 or 3 \& 5 or 5 \& 6) follow. Since the pressure drop across the cell is fixed, the overall flow rate increases as the bodies erode. This can be seen by the overall vorticity magnitude growing in time. By the final frame shown, body 4 has vanished completely and our method handles this event seamlessly.
